---
title: "Toulmin Diagram"
author: "Russell Almond"
date: "`r Sys.Date()`"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
```

## Base Graph

```{r toulminNodes}
toulminNodes <- 
  create_node_df(
    n=6,
    type=c("a","a","a","a","b","0"),
    label=c("Claim","Warrant","Alternative","Observation","Context",""),
    shape=c(rep("rectangle",5),"none"),
    style=c("rounded","rounded","rounded","rounded","dotted"),
    x=c(200,100,300,200,200,200),
    y=c(100,200,200,300,400,200)
  )
toulminEdges <- 
  create_edge_df(
    from=c(1,2,3,6,5,5,5),
    to=c(6,6,6,4,2,3,4),
    rel=c("0","1","1","1","2","2","2"),
    arrowhead=c("none",rep("normal",6)),
    style=c(rep("solid",4),rep("dashed",3))
  )
toulminGraph <-
  create_graph(toulminNodes,toulminEdges)
```

## Print it

```{r render}
render_graph(toulminGraph)
```

  






You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



